### 2019-10-05 README.Rmd
readme/pkgdown updates + appveyor tweak

__Authors:__ [Nima Hejazi](https://nimahejazi.org) and [Mark van der
  Laan](https://vanderlaan-lab.org)

@@

To contribute, install the bleeding-edge _development version_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-master-installation, eval = FALSE}
devtools::install_github("nhejazi/methyvim")
```

@@

```{r gh-develop-installation, eval = FALSE}
devtools::install_github("nhejazi/methyvim", ref = "RELEASE_3_6")
```

@@

>>>>

__Authors:__ [Nima Hejazi](https://nimahejazi.org) and [Mark van der
  Laan](https://vanderlaan-lab.org/about)

@@

To contribute, install the bleeding-edge _development version_ from GitHub via
[`remotes`](https://CRAN.R-project.org/package=remotes):

```{r gh-master-installation, eval = FALSE}
remotes::install_github("nhejazi/methyvim")
```

@@

```{r gh-develop-installation, eval = FALSE}
remotes::install_github("nhejazi/methyvim", ref = "RELEASE_3_6")
```

@@

        @manual{hejazi2019methyvimbioc,
          author = {Hejazi, Nima S and {van der Laan}, Mark J},
          title = {{methyvim}: Targeted, robust, and model-free differential
            methylation analysis},
          doi = {10.18129/B9.bioc.methyvim},
          url = {https://bioconductor.org/packages/methyvim},
          note = {R package version 1.6.0}
        }
